\documentclass[11pt]{article}

% Font and color stuff for text
\usepackage{xcolor}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

% Paragraph formatting
\setlength{\parindent}{0pt} 
\setlength{\parskip}{0.125cm} 

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

% Checkboxes
\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}

% A macro used to make the What I Know Section look "good"
\newcommand{\iknow}[2]{\par\textbf{#1} \textit{#2}}

\title{A Short Report About What I Know}
\author{ Harry Litchfield }
\date{\today}

\begin{document}
\maketitle	

\section*{How to complete this assignment}
\begin{todolist}
    \item On a debian 10 droplet:
    \begin{verbatim}
        apt update
        apt install git
        apt install texlive-full
    \end{verbatim}
    \item If the droplet is new, you'll need to configure git again.
    \item Fork the repo
    \item Clone your fork to your machine ( use https or ssh, whichever one you like better )
    \item if the droplet is new and you want to use ssh, you'll need to generate a new key pair
    \item In the repo, create a directory called YourName
    \item Copy the MyReport.tex file into your directory.
    \item Use vim to fill out the "to do"s in the "What I Know" section.
    \item Change "Author" to your name.
    \item Compile using
    \begin{verbatim}
        pdflatex MyReport.tex
    \end{verbatim}
    \item If all goes well, you will see a "MyReport.pdf" in the directory!
    \item \textcolor{red}{ git add MyReport.tex}
    \item {\Large\textcolor{red}{ DO NOT git add -A or git add MyReport.pdf!}}
    \item {\LARGE\textcolor{red}{ DO NOT git add -A or git add MyReport.pdf!}}
    \item I don't want your pdf going onto github, only your .tex  file
    \item Make a pull request
    \item Use sftp to get your pdf to your home computer
    \item Submit the pdf on blackboard
    \item 50 pts for successful PR
    \item 50 pts for PDF
\end{todolist}

\section*{What I Know}

\noindent\textit{Below is a list of a few commands I know, along with brief descriptions of what they do.}
\iknow{cp}{This command is for copying files}
\iknow{cp -r}{This command is for copying directories}
\iknow{mv}{This command is for moving files from directory to another}
\iknow{rm}{This command is for removing a file}
\iknow{rm -r}{This command is for removing a directory}
\iknow{ls -a}{This command is for listing all files in a directory including hidden files}
\iknow{ls -al}{This command is for list all files in a directory including the hidden files in a long format}
\iknow{ls -l}{This command is for listing all files except the hidden ones in a directory in a long format}
\iknow{ssh}{This command allows you to connect remotely to another computer}
\iknow{ssh-keygen}{This command creates a ssh key genrated pair so you can access your computer remotely}
\iknow{cd}{This command is for changing directory}
\iknow{cd ../}{This command will take you back to the previous directory}
\iknow{cd \textasciitilde}{This command will take you to the home directory}
\iknow{echo}{This command will display the text used with the command}
\iknow{cat}{This command is short for concatenate can do multiple this it can read from a file with cat filename, write and overwrite a file with cat f1 >(>>) f2 }
\iknow{adduser}{This command allows you to add a user to your server}
\iknow{deluser}{This command allows you to delete a user from your server}
\iknow{chmod}{This command allows you to modify the permissions on a file so other users can only read and not write etc}
\iknow{chown}{This command allows you change the ownership of a file or directory}

\section*{Conclusion}
Now you know a tiny bit about using \LaTeX to prepare documents! One thing cool about \LaTeX is that you make beautiful math equations

\begin{equation}
\int_{0}^{\pi}x^2\,dx
\end{equation}

and there are ways to put images in your documents, and code snippets, and you can produce really beautifully formatted PDFs. The lecture notes for this class were all made on an Ubuntu laptop, with vim, in the terminal. And I daresay they are way more beautiful that what could have been easily made with Microsoft Word.

\end{document}
